---
title: "explore-ideas"
output: html_document
---




# Sentiment


## Random thoughts how to calculate proportions in long data

```{r}
library(tidyverse)

sentiment_txt_data_tidy <- sentiment_txt_data %>% 
  tidy_sentiment_txt()

select_sentiments <- c("anticipation", "positive", "negative", "sadness", "fear", "joy", "anger", "disgust", "surprise")

sentiment_txt_data_tidy %>% 
  select(date, super, division2, 
         anticipation, positive, negative, sadness, fear, joy, anger, disgust, surprise) %>% 
  pivot_longer(cols = c(sentiments), 
               names_to = "sentiment_name", 
               values_to = "sentiment_check") %>% 
  group_by(date, super, division2) %>% 
  mutate(sum_sentiments = sum(sentiment_check))


sentiment_txt_data_tidy %>% 
        tidyr::unnest(cols = all_sentiments) %>% 
        dplyr::select(date, all_sentiments, super, division2) %>% 
        tidyr::drop_na() %>% 
  dplyr::arrange(date) %>% 
  dplyr::group_by(date, super, division2) %>% 
  dplyr::mutate(n_sentiment_distinct = n_distinct(all_sentiments))
```





## Chris' idea with rolling mean

Works but not really easy to:

1. generalise to other variables 
1. calculate proportions based on "filtering" variables like division or category

```{r}
#ADD CHRIS ROLLING MEAN LINE GRAPH HERE


# Define rolling mean function
rolling_mean <- tibbletime::rollify(mean, window = 30)


mean_data <- purrr::map(c("anger", "anticipation", "disgust", "fear", "joy", "negative",
                          "positive", "sadness", "surprise", "trust"), function(x) {
                            
                            sentiment_txt_data_tidy %>%
                              dplyr::group_by(date) %>%
                              dplyr::summarise(var_sum = sum(.data[[x]], na.rm = TRUE)) %>%
                              dplyr::ungroup() %>%
                              tsibble::tsibble(index = date) %>%
                              tsibble::fill_gaps(var_sum = 0) %>%
                              as.data.frame() %>%
                              dplyr::mutate(roll_var = rolling_mean(var_sum)) %>%
                              dplyr::select(roll_var) %>%
                              purrr::set_names(x)
                          }) %>%
  do.call(cbind, .)

to_plot <- dplyr::bind_cols(
  sentiment_txt_data_tidy %>%
    dplyr::group_by(date) %>%
    dplyr::summarise(var_sum = sum(anger, na.rm = TRUE)) %>%
    dplyr::ungroup() %>%
    tsibble::tsibble(index = date) %>%
    tsibble::fill_gaps(var_sum = 0) %>%
    as.data.frame() %>%
    dplyr::select(date),
  as.data.frame(prop.table(as.matrix(mean_data), 1) * 100)
)

to_plot %>%
  tidyr::drop_na() %>%
  tidyr::pivot_longer(-date) %>%
  ggplot2::ggplot(ggplot2::aes(x = date,
                               y = value,
                               colour = name,
                               group = name)) +
  ggplot2::geom_line()

```


## Density plot

Works but shows someting different to proportions and might not be what we (or users) are actually interested in

Need to look into this approach `ggplot2::geom_freqpoly(y = (..count..)/sum(..count..)) +` and figure out how exactly it is working


```{r}
library(tidyverse)
library(scales)

experiencesdashboard::sentiment_txt_data %>% 
  mutate(date = lubridate::as_date(date)) %>% 
  tidyr::unnest(cols = all_sentiments) %>% 
  dplyr::select(date, all_sentiments) %>% 
  tidyr::drop_na() %>% 
  ggplot2::ggplot(ggplot2::aes(x = date, 
                               fill = all_sentiments,
                               colour = all_sentiments)) +
  ggplot2::geom_density(alpha = .1, size = 1) +
  # ggplot2::geom_freqpoly(y = (..count..)/sum(..count..)) +
  ggplot2::scale_x_date() +
  ggplot2::scale_fill_viridis_d(direction = -1) +
  ggplot2::scale_colour_viridis_d(direction = -1) +
  ggplot2::labs(x = "Date", 
                y = NULL, 
                fill = "Selected\nsentiments",
                colour = "Selected\nsentiments") +
  ggplot2::theme(text = ggplot2::element_text(size = 16))
```







